Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-13 tex/paper.tex
Remove some references
Add final figure
Fix references

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on
1,000 new images per digit (test set of 10,000 images).
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure \ref{fig:accplot}. This trained network achieved an
accuracy of 94\% and very quickly converged after five iterations of training. An example
classification of an image with the activations and learned filters is presented
in Figure \ref{fig:actfilts}. Figure [?] shows examples of correctly and incorrectly classified images.

@@

The second experiment with the one convolutional/pooling layer architecture was also trained
for 50 iterations but with 100 images per digit instead of 50 (training set of 1,000 images).
This trained network was then tested on 1,000 new images per digit (test set of 10,000 images).
The results of this training can be seen in Figure \ref{fig:accplot}.This trained network
achieved an accuracy of 93.22\% and also quickly converged after about five iterations of training.
Figure [?] shows examples of correctly and incorrectly classified images.

@@

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on 1,000 new images per digit
(test set of 10,000 images).
The training images were taken from the easier portion of the training set,
while the test images were taken from both sets.
The results of this training can be seen in Figure \ref{fig:accplot}. This trained network achieved an accuracy of 92.8\% converging after about 10 iterations of training.
An example classification of an image with the activations and learned filters is presented
in Figure \ref{fig:actfilts}.
Figure [?] shows examples of correctly and incorrectly classified images.

@@

Our two convolutional/pooling layer architecture (trained with 500 images) did not significantly outperform
our one convolutional/pooling layer (also trained with 500 images) on the MNIST dataset. In fact, while both nets
performed similarly after 50 iterations of training (to a difference of 1\%), the deeper architecture took more
training iterations to converge, as can be seen on the left side of \ref{fig:accplot}.
This makes it tempting to conclude that a deep network may not be appropriate for this classification task.

@@

While analyzing the digits that are misclassified by our nets, we noticed that there are a sizable number of
digits that are difficult even for humans to discern (see Figure [?] for examples). Our net also seems to have
significant trouble with discerning the number 8, possibly because it has much in common with multiple other
digits like 6 and 9, especially when squished. We feel that training on deformed versions of input images
(say, squished versions of 8's) would significantly improve our net's performance on these digits.

@@

>>>>

The one convolutional/pooling layer architecture was trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on
1,000 new images per digit (test set of 10,000 images).
The training images were taken from the easier portion of the training set, while the test images were taken from
both sets. The results of this training can be seen in Figure \ref{fig:accplot}. This trained network achieved an
accuracy of 94\% and very quickly converged after five iterations of training. An example
classification of an image with the activations and learned filters is presented
in Figure \ref{fig:actfilts}. Figure \ref{fig:misclassify} shows examples of correctly and incorrectly classified images.

@@

The second experiment with the one convolutional/pooling layer architecture was also trained
for 50 iterations but with 100 images per digit instead of 50 (training set of 1,000 images).
This trained network was then tested on 1,000 new images per digit (test set of 10,000 images).
The results of this training can be seen in Figure \ref{fig:accplot}.This trained network
achieved an accuracy of 93.22\% and also quickly converged after about five iterations of training.

@@

The two convolutional/pooling layer architecture was also trained for 50 iterations with 50 images per digit
(training set of 500 images), and was subsequently tested on 1,000 new images per digit
(test set of 10,000 images).
The training images were taken from the easier portion of the training set,
while the test images were taken from both sets.
The results of this training can be seen in Figure \ref{fig:accplot}. This trained network achieved an accuracy of 92.8\% converging after about 10 iterations of training.
An example classification of an image with the activations and learned filters is presented
in Figure \ref{fig:actfilts}.

@@

Our two convolutional/pooling layer architecture (trained with 500 images) did not significantly outperform
our one convolutional/pooling layer (also trained with 500 images) on the MNIST dataset. In fact, while both nets
performed similarly after 50 iterations of training (to a difference of 1\%), the deeper architecture took more
training iterations to converge, as can be seen on the left side of Figure \ref{fig:accplot}.
This makes it tempting to conclude that a deep network may not be appropriate for this classification task.

@@

While analyzing the digits that are misclassified by our nets, we noticed that there are a sizable number of
digits that are difficult even for humans to discern (see Figure \ref{fig:misclassify} for examples). Our net also seems to have
significant trouble with discerning the number 8, possibly because it has much in common with multiple other
digits like 6 and 9, especially when squished. We feel that training on deformed versions of input images
(say, squished versions of 8's) would significantly improve our net's performance on these digits.

@@

\begin{figure*}
  \makebox[\textwidth][c]{\includegraphics[scale=0.72]{misclassify}}
  \caption{This is a tiger. Rawr!}
  \label{fig:misclassify}
\end{figure*}
